Performance and Development Review

### 2015-11-24 papers/PDR.tex
Empirical studies of the eigenvalues and eigenvectors of a correlation matrix.

\section{Career}
\begin{itemize}
\item My aspiration is to work in the industry and apply the methods
  and knowledge learned during my Ph.D studies.
\item I hope to have opportunities of working as a summer internship
  in a major investment bank or hedge fund.
\end{itemize}

>>>>

\section{Career}
\begin{itemize}
\item My aspiration is to work in the industry and apply the methods
  and knowledge developed during my Ph.D studies.
\item I hope to have opportunities of working as a summer internship
  at a role of quantitative analysis.
\end{itemize}
